---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stolz15 - Implementation of Stolzenburg's (2015) Periodicity Algorithm

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

Periodicity, also known as harmonicity, 
is an important predictor of a chord's consonance.
This package implements Stolzenburg's (2015) algorithm
for quantifying a chord's periodicity.

## Installation 

You can install this package from GitHub:

```r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("pmcharrison/stolz15")
```

## Example usage

Higher model outputs correspond to greater period lengths
and hence lower periodicity.
A major chord therefore produces a lower score than a diminished chord:

```{r}
library(stolz15)

smooth_log_periodicity(c(60, 64, 67))
smooth_log_periodicity(c(60, 63, 66))
```

## References

Stolzenburg, F. (2015). Harmony perception by periodicity detection. Journal of Mathematics and Music, 9(3), 215–238. https://doi.org/10.1080/17459737.2015.1033024
